
\documentclass[a4paper,8pt]{article}

\usepackage{parskip} 
\usepackage{hologo}
\usepackage{fontspec}

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9, top=.4in, bottom=.4in]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.42\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{1pt}{2pt}{2pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\color[HTML]{110223}%{1C033C}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}
% \usepackage{times}

% For underline
\usepackage[normalem]{ulem}

\setmainfont{Arial}  % Set it to whatever you like

\begin{document}

% non-numbered pages
\pagestyle{empty} 


\begin{tabularx}{\linewidth}{@{} C @{}}
\color[HTML]{1C033C} \Huge{Aditya Kumar Gupta} \\[6pt]
\\
\textcolor[HTML]{371e77}{\underline{\href{mailto:ag2532460@gmail.com}{\raisebox{-0.05\height}{\faEnvelope} ag2532460@gmail.com}} $|$}
\textcolor[HTML]{371e77}{\underline{\href{mailto:aditya.2024ec1188@kiet.edu}{\raisebox{-0.05\height}{\faEnvelope} aditya.2024ec1188@kiet.edu}} $|$}
\textcolor[HTML]{371e77}{\href{tel:+918318354172}{\raisebox{-0.05\height}{\faMobile} +918318354172}}

\textcolor[HTML]{371e77}{\underline{\href{https://github.com/adityaec2024}{\raisebox{-0.05\height}{\faGithub} github.com/adityaec2024}} $|$}
\textcolor[HTML]{371e77}{\underline{\href{https://www.linkedin.com/in/aditya-kumar-gupta-44671123b/}{\raisebox{-0.05\height}{\faLinkedin} linkedin.com/in/aditya-kumar-gupta-44671123b/}}}
\end{tabularx}

% Education
\section{Education}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{KIET Group of Instituions} & \hfill \color[HTML]{371e77} Expected graduation date: Jun. 2024 \\
\color[HTML]{371e77} B.Tech. in Electronics and Communication Engineering  & \hfill \color[HTML]{4B28A4} \textit{\textbf{Percentage: 73.58}} \\
\color[HTML]{1C033C} \textbf{Kisan Intermediate College} & \hfill \color[HTML]{371e77}  \\
\color[HTML]{371e77} Senior Secondary(CBSE)  & \hfill \color[HTML]{4B28A4} \textit{\textbf{Percentage: 60.00}} \\
\color[HTML]{1C033C} \textbf{P.G. Senior Secondary School} & \hfill \color[HTML]{371e77} \\
\color[HTML]{371e77} Secondary(UP Board)  & \hfill \color[HTML]{4B28A4} \textit{\textbf{Percentage: 74.10}} \\
\end{tabularx}


%Experience
\section{Internship}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{\uline{\href{https://adityaec2024.github.io/MyPortfolio/}{IBM(Virtual)}}} \hfill \color[HTML]{371e77} 12th June,2023  -  24th July,2023 \\[4pt]
\color[HTML]{371e77}\textbf{\textit{Frontend Development}}\ \hfill \color[HTML]{4B28A4} \textit{HTML and CSS} \\[5pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Responsible for developing Frontend web applications based on HTML, CSS and JavaScript.
        \item Independently tackled the challenge of crafting a responsive 
  website tailored for mobile platforms, and meticulously refined the CSS to achieve a more polished and efficient design.
        \item Learnt how to deploy web applications.
    \end{itemize}
\end{minipage}
\end{tabularx}

% Projects
\section{Projects}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{\uline{{}{Amazon Clone}}} \hfill \color[HTML]{371e77} Jul. 2023 - Ongoing \\[4pt]
\color[HTML]{371e77}\textbf{\textit{ Amazon clone web app }} \hfill \color[HTML]{4B28A4} \textit{ HTML and CSS} \\[5pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Developed a fully functional Amazon clone web app using HTML and CSS.
        \item Ensured seamless user experience across devices by implementing responsive design.
        \item Demonstrated strong front-end skills while working on a complex project.
    \end{itemize}
    \end{minipage}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{\uline{\href{https://adityaec2024.github.io/MyPortfolio/}{Portfolio Website}}} \hfill \color[HTML]{371e77} June 2023 \\[4pt]
\color[HTML]{371e77}\textbf{\textit{Responsive Portfolio Website}} \hfill \color[HTML]{4B28A4} \textit{  HTML and CSS} \\[5pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Responsive Design: The website is designed to adapt to various screen sizes, ensuring a great user experience on both mobile and desktop devices.
        \item Interactive Content: Engage your visitors with interactive content, including smooth scrolling, animated sections, and dynamic skill bars.
        \item About Me Section: Share your background, skills, and experience to give visitors a better understanding of who you are.
    \end{itemize}
    \end{minipage}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{\uline{\href{https://github.com/adityaec2024/Automated-Watering-Plant}{Automated Watering Plant}}} \hfill \color[HTML]{371e77} Jan 2023 \\[4pt]
\color[HTML]{371e77}\textbf{\textit{ A Cutting-edge Automated Watering System}} \hfill \color[HTML]{4B28A4} \textit{ Nano Arduino, Relay, and Soil Moisture sensors} \\[5pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Implemented a cutting-edge automated watering system that delivers moisture to plants at specific intervals.
        \item Designed to optimize plant growth by ensuring they receive water only when needed.
        \item Streamlined plant care and minimized the risk of over or under-watering.
        \item Demonstrated a proficiency in working with trending technologies in the field of plant care.
    \end{itemize}
    \end{minipage}
\end{tabularx}

\section{Skills}
\color[HTML]{1C033C}\textbf{Languages:} \\[2pt]
\color[HTML]{371e77} \hspace*{4ex} : C, C++, HTML, CSS\\[3pt]
\color[HTML]{1C033C}\textbf{Oother Skills:} \\[2pt]
\color[HTML]{371e77} \hspace*{4ex} : Competitive Programming, Data Structures, Algorithm, OOPS, DBMS, Basics of CN\\[3pt]

\section{Awards and Achievements}
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Geeksforgeeks handle:\color[HTML]{1C033C} \textbf{\uline{\href{https://auth.geeksforgeeks.org/user/aditya2024ec1188/practice}{ aditya2024ec}}} (110+ Question Solved), 95+ Days Daily Streak
        \item LeetCode handle: \color[HTML]{1C033C} \textbf{\uline{\href{https://leetcode.com/GuptaAditya/}{  GuptaAditya/}}} (220+ Question Solved), 180+ Days Daily Streak
          \item Hackerrank handle: \color[HTML]{1C033C} \textbf{\uline{\href{https://www.hackerrank.com/profile/aditya_2024ec111}{aditya2024}}} 5 Star at C++
            \item Achieved 9th rank in KICCS-D-HACK (Intra college coding competition) at college level. \color[HTML]{1C033C} \textbf{\uline{\href{https://drive.google.com/drive/folders/15AbsP8XsAV-0P0dnc_scWvhQ8lN_f9Te}{(link)}}}
         \item Achieved 1st rank in KICCS-D-HACK (Intra College Coding Competition) at Department Level.\color[HTML]{1C033C} \textbf{\uline{\href{https://drive.google.com/file/d/1sx484v3mJco3uMW3SRO0vheVhteHdej2/view}{(link)}}}
          \item Participated in college INNOTECH.\color[HTML]{1C033C} \textbf{\uline{\href{https://drive.google.com/file/d/1ZzpOOnrAgG7Rz4Oe_1szO-2hdGB0emJZ/view}{(link)}}}\color[HTML]{1C033C} \textbf{\uline{\href{https://drive.google.com/file/d/1x053AQw_YBLsiAtNdGqWPba4uYvAWS6U/view}{(link)}}}
    \end{itemize}
    \end{minipage}
\end{document}
